\section{Conclusion}

The Carry Protocol represents a pivotal leap forward in the confluence of games and advertising within the burgeoning web3 domain. By introducing a structured and transparent framework for integrating ads into the game experience, Carry not only unlocks a new revenue stream for developers but also paves the way for advertisers to reach a dynamic and engaged audience.

Central to this is the concept of slots — dynamic spaces within games that can host various types of advertisements. The Carry Protocol's meticulous design ensures that these slots integrate seamlessly with the game interface, ensuring that advertising is both organic and engaging.

The robust governance structure proposed ensures the protocol's continuous evolution, adapting to the ever-evolving landscape of games and digital advertising. Moreover, the emphasis on data-driven insights, facilitated through detailed metrics and experimentation capabilities, ensures that every stakeholder, from developers and advertisers to gamers, has the tools they need to extract maximum value from the system.

In a broader spectrum of game environments, particularly within fully on-chain games, slots predominantly belong to the game community or individual players. Consequently, advertising revenue is more intricately allocated to players and developers. There is a compelling rationale to anticipate that this direction represents the future of advertising.

Carry Protocol stands at the forefront of a transformative wave in the game industry. Carry's innovative approach to integrating blockchain technology into games has set a new benchmark for how games are developed, played, and experienced. By offering a comprehensive suite of tools and services, Carry is not just simplifying the incorporation of blockchain elements into games but is also pioneering a new era of game economics. The platform's ability to empower developers, enhance player engagement, and foster a sense of community and ownership among gamers signifies a paradigm shift. This shift is not just in how games are designed and monetized, but also in how they are perceived and valued by the game community.

Looking ahead, Carry's role in shaping the future of digital games is poised to be significant. As the game industry continues to evolve and expand, embracing new technologies and narratives, Carry will likely be at the heart of this evolution, driving innovation and growth. Carry is not just creating a bridge between traditional games and the blockchain world; it is paving the way for a more interconnected and immersive games universe where the potential for creativity, interaction, and economic opportunity is boundless. This is just the beginning, and the journey ahead for Carry, and the game industry as a whole, promises to be as exciting as it is transformative.