\section{Economics of Carry}

Within the Carry ecosystem, Carry token plays a role in all aspects of the economics cycle:

\textbf{Carry Token}: The primary currency of the Carry marketplace, the Carry Token facilitates all exchanges that transpire here. From purchasing ad spaces in slots to bidding on prime gaming real estate, the Carry Token is the universal medium. Yet its utility doesn't end merely at marketplace transactions. One of the pivotal functions of the Carry Token is its convertibility: users can exchange it for Carry Fuel, amplifying its significance within the protocol.

\textbf{Carry Token for Network Burning}: Think of Carry Token as the energy driving the actions within the Carry Protocol. Every operation, be it placement advertisements, transferring slots, or toggling slot statuses, consumes Carry Fuel. And once utilized, this fuel is irreversibly burned. The burning mechanism not only ensures transparency and scarcity but also provides a tangible cost to actions, which in turn deters frivolous or malicious behavior on the network.

\textbf{Carry Governance}:The Carry Protocol embraces adaptability through its Carry Improvement Proposal (CIP) mechanism. Carry token holders can initiate and vote on proposals, ensuring that the protocol evolves in line with the community's vision. This democratic approach ensures continuous relevance and responsiveness to industry needs.

The Carry Token establishes an internal economic equilibrium, where actions are not just facilitated but are also assigned real-world value. It's a delicate balance that ensures sustainability, growth, and fairness in the Carry universe.

\subsection{Carry Token Utilization Scenarios}

\begin{table}[!htb]
    \centering
    \begin{tabular}{c|c|c}
        \toprule
        Scenatio & Type & Add Value \\
        \midrule
        \rule{0pt}{2ex} 
        Slot placement durations auction & Token &Transaction fees discount  \\
        \rule{0pt}{2ex} 
        Ad Content Placement & GAS &  \\
        \rule{0pt}{2ex} 
        Slot Initialization &GAS& \\
        \rule{0pt}{2ex} 
        Effect tracking & Token & \\
        \rule{0pt}{2ex} 
        Slot settlement  & Token & \\
        \rule{0pt}{2ex} 
        Issue a Proposal & Gvernance & \\
        \rule{0pt}{2ex} 
        Vote on snapshot & Governance & Staking Rewards\\
        %... add more rows as necessary
        \bottomrule
    \end{tabular}
    \caption{Carry Token Utilizations}
    \label{table:example}
\end{table}